








\section*{ID: 4de87c9a}
3 more than 8 times a number $x$ is equal to 83 . Which equation represents this situation?\\
A. $(3)(8) x=83$\\
B. $8 x=83+3$\\
C. $3 x+8=83$\\
D. $8 x+3=83$\\
$a(3-x)-b=-1-2 x$

In the equation above, $a$ and $b$ are constants. If the equation has infinitely many solutions, what are the values of $a$ and $b$ ?\\
A. $a=2$ and $b=1$\\
B. $a=2$ and $b=7$\\
C. $a=-2$ and $_{b=5}$\\
D. $a=-2$ and $b=-5$

\section*{ID: e7b6f0d1}
$$
4 x+6=18
$$

Which equation has the same solution as the given equation?\\
A. $4 x=108$\\
B. $4 x=24$\\
C. $4 x=12$\\
D. $4 x=3$

$$
2(k x-n)=-\frac{28}{15} x-\frac{36}{19}
$$

In the given equation, $k$ and $n$ are constants and $n>1$. The equation has no solution. What is the value of $k$ ?

\section*{ID: f09097b1}
An agricultural scientist studying the growth of corn plants recorded the height of a corn plant at the beginning of a study and the height of the plant each day for the next 12 days. The scientist found that the height of the plant increased by an average of 1.20 centimeters per day for the 12 days. If the height of the plant on the last day of the study was 36.8 centimeters, what was the height, in centimeters, of the corn plant at the beginning of the study?

Nasir bought 9 storage bins that were each the same price. He used a coupon for $\$ 63$ off the entire purchase. The cost for the entire purchase after using the coupon was $\$ 27$. What was the original price, in dollars, for 1 storage bin?\\
$10=2 x+4$

How many solutions exist to the equation shown above?\\
A. None\\
B. Exactly 1\\
C. Exactly 3\\
D. Infinitely many

$$
x+40=95
$$

What value of $x$ is the solution to the given equation?

If $2 x=12$, what is the value of $9 x$ ?

$$
5(t+3)-7(t+3)=38
$$

What value of $t$ is the solution to the given equation?

\section*{ID: 620abf36}
If $5(x+4)=4(x+4)+29$, what is the value of $x+4$ ?\\
A. -4\\
B. 25\\
C. 29\\
D. 33

\section*{ID: ed18c4f7}
Cathy has $n$ CDs. Gerry has 3 more than twice the number of CDs that Cathy has. In terms of $n$, how many CDs does Gerry have?\\
A. $3 n-2$\\
B. $3 n+2$\\
C. $2 n-3$\\
D. $2 n+3$

If $x=7$, what is the value of $x+20$ ?\\
A. 13\\
B. 20\\
C. 27\\
D. 34

A gym charges its members a onetime $\$ 36$ enrollment fee and a membership fee of $\$ 19$ per month. If there are no charges other than the enrollment fee and the membership fee, after how many months will a member have been charged a total of $\$ 188$ at the gym?\\
A. 4\\
B. 5\\
C. 8\\
D. 10

If $7 x=28$, what is the value of $8 x$ ?\\
A. 21\\
B. 32\\
C. 168\\
D. 224

Townsend Realty Group Investments

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Property address & Purchase price (dollars) & Monthly rental price (dollars) \\
\hline
Clearwater Lane & 128,000 & 950 \\
\hline
Driftwood Drive & 176,000 & 1,310 \\
\hline
Edgemont Street & 70,000 & 515 \\
\hline
Glenview Street & 140,000 & 1,040 \\
\hline
Hamilton Circle & 450,000 & 3,365 \\
\hline
\end{tabular}
\end{center}

The Townsend Realty Group invested in the five different properties listed in the table above. The table shows the amount, in dollars, the company paid for each property and the corresponding monthly rental price, in dollars, the company charges for the property at each of the five locations. Townsend Realty purchased the Glenview Street property and received a $40 \%$ discount off the original price along with an additional $20 \%$ off the discounted price for purchasing the property in cash. Which of the following best approximates the original price, in dollars, of the Glenview Street property?\\
A. $\$ 350,000$\\
B. $\$ 291,700$\\
C. $\$ 233,300$\\
D. $\$ 175,000$

\section*{ID: eac739b2}
If $4 x+2=12$, what is the value of $16 x+8$ ?\\
A. 40\\
B. 48\\
C. 56\\
D. 60

\section*{ID: d9d83c02}
For what value of $w$ does $w-10=2(w+5)$ ?\\
A. 5\\
B. 0\\
C. -15\\
D. -20

$$
2(p+1)+8(p-1)=5 p
$$

What value of $p$ is the solution of the equation above?

If $6+x=9$, what is the value of $18+3 x$ ?

\section*{ID: Ocb57740}
Each side of a 30 -sided polygon has one of three lengths. The number of sides with length 8 centimeters (cm) is 5 times the number of sides $n$ with length 3 cm . There are 6 sides with length 4 cm . Which equation must be true for the value of $n$ ?\\
A. $5 n+6=30$\\
B. $6 n+6=30$\\
C. $8 n+3 n+4 n=30$\\
D. $8(5 n)+3 n+4(6)=30$

ID: ce314070\\
If $4 x-\frac{1}{2}=-5$, what is the\\
value of $8 x-1$ ?\\
A. 2\\
B. $-\frac{9}{8}$\\
c. $-\frac{5}{2}$\\
D. -10

$$
-3 x+21 p x=84
$$

In the given equation, $p$ is a constant. The equation has no solution. What is the value of $p$ ?\\
A. 0\\
B. $\frac{1}{7}$\\
C. $\frac{4}{3}$\\
D. 4

If $2(3 t-10)+t=40+4 t$, what is the value of $3 t ?$

\section*{ID: aee9fd2d}
If $\frac{x+6}{3}=\frac{x+6}{13}$, the value of $x+6$ is between which of the following pairs of values?\\
A. -7 and -3\\
B. -2 and 2\\
C. 2 and 7\\
D. 8 and 13

If $\frac{2 n}{5}=10$, what is the value of $2 n-1$ ?\\
A. 24\\
B. 49\\
C. 50\\
D. 99

\section*{ID: 9ff10b3b}
If $\frac{1}{2} x-\frac{1}{6} x=1$, what is\\
the value of $x$ ?\\
A. -4\\
B. $\frac{1}{3}$\\
C. 3\\
D. 6

If $2+x=60$, what is the value of $16+8 x$ ?

Megan's regular wage at her job is $p$ dollars per hour for the first 8 hours of work in a day plus 1.5 times her regular hourly wage for work in excess of 8 hours that day. On a given day, Megan worked for 10 hours, and her total earnings for that day were $\$ 137.50$. What is Megan's regular hourly wage?\\
A. $\$ 11.75$\\
B. $\$ 12.50$\\
C. $\$ 13.25$\\
D. $\$ 13.75$

If $3 x+2=8$, what is the value of $9 x+6$ ?

$$
k+12=336
$$

What is the solution to the given equation?\\
A. 28\\
B. 324\\
C. 348\\
D. 4,032

$$
66 x=66 x
$$

How many solutions does the given equation have?\\
A. Exactly one\\
B. Exactly two\\
C. Infinitely many\\
D. Zero

The equation $9 x+5=a(x+b)$, where $a$ and $b$ are constants, has no solutions. Which of the following must be true?\\
l. $a=9$\\
II. $b=5$\\
III. $b \neq \frac{5}{9}$\\
A. None\\
B. I only\\
C. I and II only\\
D. I and III only

\section*{ID: fbb0ea7f}
A rocket contained 467,000 kilograms (kg) of propellant before launch. Exactly 21 seconds after launch, $362,105 \mathrm{~kg}$ of this propellant remained. On average, approximately how much propellant, in kg, did the rocket burn each second after launch?\\
A. 4,995\\
B. 17,243\\
C. 39,481\\
D. 104,895

\section*{ID: c3989ef8}
Henry receives a $\$ 60.00$ gift card to pay for movies online. He uses his gift card to buy 3 movies for $\$ 7.50$ each. If he spends the rest of his gift card balance on renting movies for $\$ 1.50$ each, how many movies can Henry rent?\\
A. 10\\
B. 25\\
C. 35\\
D. 40

\section*{ID: 5ad9eff0}
The width of a rectangular dance floor is $w$ feet. The length of the floor is 6 feet longer than its width. Which of the following expresses the perimeter, in feet, of the dance floor in terms of $w$ ?\\
A. $2 w+6$\\
B. $4 w+12$\\
C. $w^{2}+6$\\
D. $w^{2}+6 w$

A librarian has 43 books to distribute to a group of children. If he gives each child 2 books, he will have 7 books left over. How many children are in the group?\\
A. 15\\
B. 18\\
C. 25\\
D. 29

ID: e53870b6\\
$6 x+k=6 x+5$

In the given equation, $k$ is a constant. If the equation has infinitely many solutions, what is the value of $k$ ?

\section*{ID: 628300a9}
A science teacher is preparing the 5 stations of a science laboratory. Each station will have either Experiment A materials or Experiment B materials, but not both. Experiment A requires 6 teaspoons of salt, and Experiment B requires 4 teaspoons of salt. If $x$ is the number of stations that will be set up for Experiment $A$ and the remaining stations will be set up for Experiment B, which of the following expressions represents the total number of teaspoons of salt required?\\
A. $5 x$\\
B. $10 x$\\
C. $2 x+20$\\
D. $10 x+20$

\section*{ID: 45bba652}
If $2(x-5)+3(x-5)=10$, what is\\
the value of $x-5$ ?\\
A. 2\\
B. 5\\
C. 7\\
D. 12

$$
\frac{1}{4}(x+5)-\frac{1}{3}(x+5)=-7
$$

What value of $x$ is the solution to the given equation?\\
A. -12\\
B. -5\\
C. 79\\
D. 204

If $5 x=20$, what is the value of $15 x$ ?\\
A. 7\\
B. 12\\
C. 23\\
D. 60

\section*{ID: a9c04a21}
What is the solution to the equation $2 x+3=7$ ?\\
A. 1\\
B. 1.5\\
C. 2\\
D. 4

\section*{ID: 6fa593f1}
If $x=40$, what is the value of $x+6$ ?\\
A. 34\\
B. 40\\
C. 46\\
D. 64

\section*{ID: 8c515062}
A candle is made of 17 ounces of wax. When the candle is burning, the amount of wax in the candle decreases by 1 ounce every 4 hours. If 6 ounces of wax remain in this candle, for how many hours has it been burning?\\
A. 3\\
B. 6\\
C. 24\\
D. 44


