
Note: Figure not drawn to scale.

For the triangle shown, which expression represents the value of $a$ ?\\
A. $\sqrt{21^{2}-6^{2}}$\\
B. $21^{2}-6^{2}$\\
C. $\sqrt{21-6}$\\
D. $21-6$









\section*{ID: ffe862a3}
An isosceles right triangle has a hypotenuse of length 58 inches. What is the perimeter, in inches, of this triangle?\\
A. $29 \sqrt{2}$\\
B. $58 \sqrt{2}$\\
C. $58+58 \sqrt{2}$\\
D. $58+116 \sqrt{2}$

An isosceles right triangle has a perimeter of $94+94 \sqrt{2}$ inches. What is the length, in inches, of one leg of this triangle?\\
A. 47\\
B. $47 \sqrt{2}$\\
C. 94\\
D. $94 \sqrt{2}$

\section*{ID: 0e709a29}
$$
\begin{aligned}
R S & =440 \\
S T & =384 \\
T R & =584
\end{aligned}
$$

The side lengths of right triangle $R S T$ are given. Triangle $R S T$ is similar to triangle $U V W$, where $S$ corresponds to $V$ and $T$ corresponds to $W$. What is the value of $\tan W$ ?\\
A. $\frac{48}{73}$\\
B. $\frac{55}{73}$\\
C. $\frac{48}{55}$\\
D. $\frac{55}{48}$

A right triangle has legs with lengths of 24 centimeters and 21 centimeters. If the length of this triangle's hypotenuse, in centimeters, can be written in the form $3 \sqrt{d}$, where $d$ is an integer, what is the value of $d$ ?

$$
\begin{aligned}
R S & =20 \\
S T & =48 \\
T R & =52
\end{aligned}
$$

The side lengths of right triangle $R S T$ are given. Triangle $R S T$ is similar to triangle $U V W$, where $S$ corresponds to $V$ and $T$ corresponds to $W$. What is the value of $\tan W$ ?\\
A. $\frac{5}{13}$\\
B. $\frac{5}{12}$\\
C. $\frac{12}{13}$\\
D. $\frac{12}{5}$

In triangle $R S T$ above, point $W$ (not shown) lies on $\overline{R T}$. What is the value of $\cos (\angle R S W)-\sin (\angle W S T)$ ?

\section*{ID: 9ec76b54}
A right triangle has legs with lengths of 28 centimeters and 20 centimeters. What is the length of this triangle's hypotenuse, in centimeters?\\
A. $8 \sqrt{6}$\\
B. $4 \sqrt{74}$\\
C. 48\\
D. 1,184

\section*{ID: 6ab30ce3}
Triangle $A B C$ is similar to triangle $D E F$, where $A$ corresponds to $D$ and $C$ corresponds to $F$. Angles $C$ and $F$ are right angles. If $\tan (A)=\sqrt{3}$ and $D F=125$, what is the length of $\overline{D E}$ ?\\
A. $125 \frac{\sqrt{3}}{3}$\\
B. $125 \frac{\sqrt{3}}{2}$\\
C. $125 \sqrt{3}$\\
D. 250

\section*{ID: bf8d843e}
In $\triangle A B C$ above, what is the length of $\overline{A D}$ ?\\
A. 4\\
B. 6\\
C. $6 \sqrt{2}$\\
D. $6 \sqrt{3}$

The length of a rectangle's diagonal is $3 \sqrt{17}$, and the length of the rectangle's shorter side is 3 . What is the length of the rectangle's longer side?

\section*{ID: c9f8d1e9}
Note: Figure not drawn to scale.

For the right triangle shown, $a=4$ and $b=5$. Which expression represents the value of $c$ ?\\
A. $4+5$\\
B. $\sqrt{(4)(5)}$\\
C. $\sqrt{4+5}$\\
D. $\sqrt{4^{2}+5^{2}}$

\section*{ID: a5aee181}
The length of a rectangle's diagonal is $5 \sqrt{17}$, and the length of the rectangle's shorter side is 5 . What is the length of the rectangle's longer side?\\
A. $\sqrt{17}$\\
B. 20\\
C. $15 \sqrt{2}$\\
D. 400

A square is inscribed in a circle. The radius of the circle is $\frac{20 \sqrt{2}}{2}$ inches. What is the side length, in inches, of the square?\\
A. 20\\
B. $\frac{20 \sqrt{2}}{2}$\\
C. $20 \sqrt{2}$\\
D. 40

Triangle $A B C$ is similar to triangle $D E F$, where angle $A$ corresponds to angle $D$ and angles $C$ and $F$ are right angles. The length of $\overline{A B}$ is 2.9 times the length of $\overline{D E}$. If $\tan A=\frac{21}{20}$, what is the value of $\sin D$ ?

In a right triangle, the tangent of one of the two acute angles is $\frac{\sqrt{3}}{3}$. What is the tangent of the other acute angle?\\
A. $-\frac{\sqrt{3}}{3}$\\
B. $-\frac{3}{\sqrt{3}}$\\
c. $\frac{\sqrt{3}}{3}$\\
D. $\frac{3}{\sqrt{3}}$

\section*{ID: 13d9a1c3}
In the right triangle shown above, what is the length of $\overline{P Q}$ ?

\section*{ID: 2be01bd9}
Triangle $A B C$ is similar to triangle $D E F$, where angle $A$ corresponds to angle $D$ and angle $C$ corresponds to angle $F$. Angles $C$ and $F$ are right angles. If $\tan (A)=\frac{50}{7}$, what is the value of $\tan (E)$ ?

\section*{ID: dba6a25a}
In the figure above, $\overline{B D}$ is parallel to $\overline{A E}$.\\
What is the length of $\overline{C E}$ ?

In triangle $J K L, \cos (K)=\frac{24}{51}$ and angle $J$ is a right angle. What is the value of $\cos (L)$ ?

\section*{ID: 25da87f8}
A triangle with angle measures $30^{\circ}, 60^{\circ}$, and $90^{\circ}$ has a perimeter of $18+6 \sqrt{3}$.\\
What is the length of the longest side of the triangle?


