
A trivia tournament organizer wanted to study the relationship between the number of points a team scores in a trivia round and the number of hours that a team practices each week. For the study, the organizer selected 55 teams at random from all trivia teams in a certain tournament. The table displays the information for the 40 teams in the sample that practiced for at least 3 hours per week.

\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
\multirow{2}{*}{Hours practiced} & \multicolumn{3}{|c|}{Number of points per round} \\
\hline
 & 6 to 13 points & 14 or more points & Total \\
\hline
3 to 5 hours & 6 & 4 & 10 \\
\hline
More than 5 hours & 4 & 26 & 30 \\
\hline
Total & 10 & 30 & 40 \\
\hline
\end{tabular}
\end{center}

Which of the following is the largest population to which the results of the study can be generalized?\\
A. All trivia teams in the tournament that scored 14 or more points in the round\\
B. The 55 trivia teams in the sample\\
C. The 40 trivia teams in the sample that practiced for at least 3 hours per week\\
D. All trivia teams in the tournament

\section*{ID: 7ce2830a}
A psychologist designed and conducted a study to determine whether playing a certain educational game increases middle school students' accuracy in adding fractions. For the study, the psychologist chose a random sample of 35 students from all of the students at one of the middle schools in a large city. The psychologist found that students who played the game showed significant improvement in accuracy when adding fractions. What is the largest group to which the results of the study can be generalized?\\
A. The 35 students in the sample\\
B. All students at the school\\
C. All middle school students in the city\\
D. All students in the city

\section*{ID: 642519d7}
A polling agency recently surveyed 1,000 adults who were selected at random from a large city and asked each of the adults, "Are you satisfied with the quality of air in the city?" Of those surveyed, 78 percent responded that they were satisfied with the quality of air in the city. Based on the results of the survey, which of the following statements must be true?

\begin{enumerate}
  \item Of all adults in the city, 78 percent are satisfied with the quality of air in the city.
  \item If another 1,000 adults selected at random from the city were surveyed, 78 percent of them would report they are satisfied with the quality of air in the city.
  \item If 1,000 adults selected at random from a different city were surveyed, 78 percent of them would report they are satisfied with the quality of air in the city.\\
A. None\\
B. II only\\
C. I and II only\\
D. I and III only
\end{enumerate}

\section*{ID: 82dfb646}
A market researcher selected 200 people at random from a group of people who indicated that they liked a certain book. The 200 people were shown a movie based on the book and then asked whether they liked or disliked the movie. Of those surveyed, $95 \%$ said they disliked the movie. Which of the following inferences can appropriately be drawn from this survey result?\\
A. At least $95 \%$ of people who go see movies will dislike this movie.\\
B. At least $95 \%$ of people who read books will dislike this movie.\\
C. Most people who dislike this book will like this movie.\\
D. Most people who like this book will dislike this movie.

\section*{ID: aa43b41f}
Near the end of a US cable news show, the host invited viewers to respond to a poll on the show's website that asked, "Do you support the new federal policy discussed during the show?" At the end of the show, the host reported that $28 \%$ responded "Yes," and $70 \%$ responded "No." Which of the following best explains why the results are unlikely to represent the sentiments of the population of the United States?\\
A. The percentages do not add up to $100 \%$, so any possible conclusions from the poll are invalid.\\
B. Those who responded to the poll were not a random sample of the population of the United States.\\
C. There were not $50 \%$ "Yes" responses and $50 \%$ "No" responses.\\
D. The show did not allow viewers enough time to respond to the poll.

\section*{ID: 4a422e3e}
To determine the mean number of children per household in a community, Tabitha surveyed 20 families at a playground. For the 20 families surveyed, the mean number of children per household was 2.4. Which of the following statements must be true?\\
A. The mean number of children per household in the community is 2.4 .\\
B. A determination about the mean number of children per household in the community should not be made because the sample size is too small.\\
C. The sampling method is flawed and may produce a biased estimate of the mean number of children per household in the community.\\
D. The sampling method is not flawed and is likely to produce an unbiased estimate of the mean number of children per household in the community.


