

\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Texting behavior & Talks on cell phone daily & Does not talk on cell phone daily & Total \\
\hline
Light & 110 & 146 & 256 \\
\hline
Medium & 139 & 164 & 303 \\
\hline
Heavy & 166 & 74 & 240 \\
\hline
Total & 415 & 384 & 799 \\
\hline
\end{tabular}
\end{center}

In a study of cell phone use, 799 randomly selected US teens were asked how often they talked on a cell phone and about their texting behavior. The data are summarized in the table above. Based on the data from the study, an estimate of the percent of US teens who are heavy texters is $30 \%$ and the associated margin of error is $3 \%$. Which of the following is a correct statement based on the given margin of error?\\
A. Approximately $3 \%$ of the teens in the study who are classified as heavy texters are not really heavy texters.\\
B. It is not possible that the percent of all US teens who are heavy texters is less than $27 \%$.\\
C. The percent of all US teens who are heavy texters is $33 \%$.\\
D. It is doubtful that the percent of all US teens who are heavy texters is $35 \%$.

\section*{ID: affb2315}
There are 55 students in Spanish club. A sample of the Spanish club students was selected at random and asked whether they intend to enroll in a new study program. Of those surveyed, $20 \%$ responded that they intend to enroll in the study program. Based on this survey, which of the following is the best estimate of the total number of Spanish club students who intend to enroll in the study program?\\
A. 11\\
B. 20\\
C. 44\\
D. 55

Views on Nuclear Energy

\begin{center}
\begin{tabular}{|c|c|}
\multicolumn{2}{c}{Use} \\
\hline
Response & Frequency \\
\hline
\begin{tabular}{c}
Strongly \\
favor \\
\end{tabular} & 56 \\
\hline
\begin{tabular}{c}
Somewhat \\
favor \\
\end{tabular} & 214 \\
\hline
\begin{tabular}{c}
Somewhat \\
oppose \\
\end{tabular} & 104 \\
\hline
\begin{tabular}{c}
Strongly \\
oppose \\
\end{tabular} & 37 \\
\hline
\end{tabular}
\end{center}

A researcher interviewed 411 randomly selected US residents and asked about their views on the use of nuclear energy. The table above summarizes the responses of the interviewees. If the population of the United States was 300 million when the survey was given, based on the sample data for the 411 US residents, what is the best estimate, in millions, of the difference between the number of US residents who somewhat favor or strongly favor the use of nuclear energy and the number of those who somewhat oppose or strongly oppose it? (Round your answer to the nearest whole number.)


























A sample consisting of 720 adults who own televisions was selected at random for a study. Based on the sample, it is estimated that $32 \%$ of all adults who own televisions use their televisions to watch nature shows, with an associated margin of error of $3.41 \%$. Which of the following is the most plausible conclusion about all adults who own televisions?\\
A. More than $35.41 \%$ of all adults who own televisions use their televisions to watch nature shows.\\
B. Between $28.59 \%$ and $35.41 \%$ of all adults who own televisions use their televisions to watch nature shows.\\
C. Since the sample included adults who own televisions and not just those who use their televisions to watch nature shows, no conclusion can be made.\\
D. Since the sample did not include all the people who watch nature shows, no conclusion can be made.







\section*{ID: e7d9649f}
A random sample of 50 people from a town with a population of 14,878 were asked to name their favorite flavor of ice cream. If 7 people in the sample named chocolate as their favorite ice-cream flavor, about how many people in the town would be expected to name chocolate?\\
A. 350\\
B. 2,100\\
C. 7,500\\
D. 10,500

\section*{ID: fc46af57}
A bag containing 10,000 beads of assorted colors is purchased from a craft store. To estimate the percent of red beads in the bag, a sample of beads is selected at random. The percent of red beads in the bag was estimated to be $15 \%$, with an associated margin of error of $2 \%$. If $r$ is the actual number of red beads in the bag, which of the following is most plausible?\\
A. $r>1,700$\\
B. $1,300<r<1,700$\\
C. $200<r<1,500$\\
D. $r<1,300$

\section*{|D: 308084c5}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Sample & Percent in favor & Margin of error \\
\hline
A & $52 \%$ & $4.2 \%$ \\
\hline
B & $48 \%$ & $1.6 \%$ \\
\hline
\end{tabular}
\end{center}

The results of two random samples of votes for a proposition are shown above. The samples were selected from the same population, and the margins of error were calculated using the same method. Which of the following is the most appropriate reason that the margin of error for sample A is greater than the margin of error for sample B?\\
A. Sample A had a smaller number of votes that could not be recorded.\\
B. Sample A had a higher percent of favorable responses.\\
C. Sample A had a larger sample size.\\
D. Sample A had a smaller sample size.

\section*{ID: f04d40b2}
From a population of 50,000 people, 1,000 were chosen at random and surveyed about a proposed piece of legislation. Based on the survey, it is estimated that $35 \%$ of people in the population support the legislation, with an associated margin of error of $3 \%$. Based on these results, which of the following is a plausible value for the total number of people in the population who support the proposed legislation?\\
A. 350\\
B. 650\\
C. 16,750\\
D. 31,750

\section*{ID: f4b3672a}
A certain forest is 253 acres. To estimate the number of trees in the forest, a ranger randomly selects 5 different 1-acre parcels in the forest and determines the number of trees in each parcel. The numbers of trees in the sample acres are 51, 59, 45, 52, and 73. Based on the mean of the sample, which of the following ranges contains the best estimate for the number of trees in the entire forest?\\
A. 11,000 to 12,000\\
B. 12,500 to 13,500\\
C. 13,500 to 14,500\\
D. 18,000 to 19,000

\section*{ID: 0108ac2d}
At a large high school, 300 students were selected at random and were asked in a survey about a menu change in the school cafeteria. All 300 students completed the survey. It was estimated that $38 \%$ of the students were in support of a menu change, with a margin of error of $5.5 \%$. Which of the following is the best interpretation of the survey results?\\
A. The percent of the students at the school who support a menu change is $38 \%$.\\
B. The percent of the students at the school who support a menu change is greater than $38 \%$.\\
C. Plausible values of the percent of the students at the school who support a menu change are between $32.5 \%$ and $43.5 \%$.\\
D. Plausible values of the number of the students at the school who support a menu change are between 295 and 305.

\section*{ID: 4096a482}
Based on a random sample from a population, a researcher estimated that the mean value of a certain variable for the population is 20.5 , with an associated margin of error of 1 . Which of the following is the most appropriate conclusion?\\
A. It is plausible that the actual mean value of the variable for the population is between 19.5 and 21.5 .\\
B. It is not possible that the mean value of the variable for the population is less than 19.5 or greater than 21.5 .\\
C. Every value of the variable in the population is between 19.5 and 21.5.\\
D. The mean value of the variable for the population is 20.5 .

\section*{ID: 9ba3e283}
In State X, Mr. Camp's eighth-grade class consisting of 26 students was surveyed and 34.6 percent of the students reported that they had at least two siblings. The average eighth-grade class size in the state is 26 . If the students in Mr. Camp's class are representative of students in the state's eighth-grade classes and there are 1,800 eighth-grade classes in the state, which of the following best estimates the number of eighth-grade students in the state who have fewer than two siblings?\\
A. 16,200\\
B. 23,400\\
C. 30,600\\
D. 46,800

\section*{ID: 1e562f24}
To estimate the proportion of a population that has a certain characteristic, a random sample was selected from the population. Based on the sample, it is estimated that the proportion of the population that has the characteristic is 0.49 , with an associated margin of error of 0.04 . Based on this estimate and margin of error, which of the following is the most appropriate conclusion about the proportion of the population that has the characteristic?\\
A. It is plausible that the proportion is between 0.45 and 0.53 .\\
B. It is plausible that the proportion is less than 0.45 .\\
C. The proportion is exactly 0.49 .\\
D. It is plausible that the proportion is greater than 0.53 .

\section*{ID: 89f8d08a}
A store manager reviewed the receipts from 80 customers who were selected at random from all the customers who made purchases last Thursday. Of those selected, 20 receipts showed that the customer had purchased fruit. If 1,500 customers made purchases last Thursday, which of the following is the most appropriate conclusion?\\
A. Exactly 75 customers must have purchased fruit last Thursday.\\
B. Exactly 375 customers must have purchased fruit last Thursday.\\
C. The best estimate for the number of customers who purchased fruit last Thursday is 75 .\\
D. The best estimate for the number of customers who purchased fruit last Thursday is 375 .

\section*{ID: 6a305cd0}
In a study, the data from a random sample of a population had a mean of 37, with an associated margin of error of 3 . Which of the following is the most appropriate conclusion that can be made about the population mean?\\
A. It is less than 37.\\
B. It is greater than 37 .\\
C. It is between 34 and 40.\\
D. It is less than 34 or greater than 40.

\begin{center}
\begin{tabular}{|c|c|}
\hline
\multicolumn{2}{|c|}{Poll Results} \\
\hline
Angel Cruz & 483 \\
\hline
Terry Smith & 320 \\
\hline
\end{tabular}
\end{center}

The table shows the results of a poll. A total of 803 voters selected at random were asked which candidate they would vote for in the upcoming election. According to the poll, if 6,424 people vote in the election, by how many votes would Angel Cruz be expected to win?\\
A. 163\\
B. 1,304\\
C. 3,864\\
D. 5,621

\section*{ID: 9ee22c16}
A random sample of 400 town voters were asked if they plan to vote for Candidate A or Candidate B for mayor. The results were sorted by gender and are shown in the table below.

\begin{center}
\begin{tabular}{|c|c|c|}
\hline
 & \begin{tabular}{c}
Plan to \\
vote for \\
Candidate \\
A \\
\end{tabular} & \begin{tabular}{c}
Plan to \\
vote for \\
Candidate \\
B \\
\end{tabular} \\
\hline
Female & 202 & 20 \\
\hline
Male & 34 & 144 \\
\hline
\end{tabular}
\end{center}

The town has a total of 6,000 voters. Based on the table, what is the best estimate of the number of voters who plan to vote for Candidate A?


