



\section*{ID: 949cd96b}
The length of the base of a certain parallelogram is $89 \%$ of the height of 
the parallelogram. Which expression represents the length of the base of the 
parallelogram, where $h$ is the height of the parallelogram?\\
A. $89 h$\\
B. $0.089 h$\\
C. $8.9 h$\\
D. 0.89 h

\section*{ID: 28c6bd8c}
Where Do People Get Most of Their Medical Information?

\begin{center}
\begin{tabular}{|l|c|}
\hline
\multicolumn{1}{|c|}{Source} & \begin{tabular}{c}
Percent of \\
those surveyed \\
\end{tabular} \\
\hline
Doctor & $63 \%$ \\
\hline
Internet & $13 \%$ \\
\hline
Magazines/brochures & $9 \%$ \\
\hline
Pharmacy & $6 \%$ \\
\hline
Television & $2 \%$ \\
\hline
Other/none of the above & $7 \%$ \\
\hline
\end{tabular}
\end{center}

The table above shows a summary of 1,200 responses to a survey question. Based on the table, how many of those surveyed get most of their medical information from either a doctor or the Internet?\\
A. 865\\
B. 887\\
C. 912\\
D. 926

Of 900,000 beads, 828,000 are silver. What percentage of the beads are silver?\\
A. $8 \%$\\
B. $36 \%$\\
C. $72 \%$\\
D. $92 \%$

\section*{ID: ba61d95f}
The population of Greenville increased by $7 \%$ from 2015 to 2016. If the 2016 population is $k$ times the 2015 population, what is the value of $k$ ?\\
A. 0.07\\
B. 0.7\\
C. 1.07\\
D. 1.7

\section*{ID: 8cbf1415}
In a group, $40 \%$ of the items are red. Of all the red items in the group, $30 \%$ also have stripes. What percentage of the items in the group are red with stripes?\\
A. $10 \%$\\
B. $12 \%$\\
C. $70 \%$\\
D. $75 \%$

A number $n$ is increased $6 \%$. If the result is 318 , what is the value of $n$ ?\\
A. 199\\
B. 299\\
C. 300\\
D. 337

\section*{ID: b2f6f17d}
A customer's monthly water bill was $\$ 75.74$. Due to a rate increase, her monthly bill is now $\$ 79.86$. To the nearest tenth of a percent, by what percent did the amount of the customer's water bill increase?\\
A. $4.1 \%$\\
B. $5.1 \%$\\
C. $5.2 \%$\\
D. $5.4 \%$

\section*{ID: 9c44f828}
There are a total of 840 seats in a school auditorium. During an assembly, students occupied $50 \%$ of the seats in the auditorium. How many seats did the students occupy during this assembly?\\
A. 25\\
B. 50\\
C. 420\\
D. 790

Isabel grows potatoes in her garden. This year, she harvested 760 potatoes and saved $10 \%$ of them to plant next year. How many of the harvested potatoes did Isabel save to plant next year?\\
A. 66\\
B. 76\\
C. 84\\
D. 86

According to the 2010 Census, the adult population aged 18 years or greater of the United States in 2010 was $234,564,071$. In 2010, a survey was conducted among a randomly chosen sample of adults aged 18 years or greater in the United States about their preference to live in a warm climate or a cool climate. The table below displays a summary of the survey results.

\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
\multicolumn{5}{|c|}{Climate Preferences} \\
\hline
 & Warm & Cool & No preference & Total \\
\hline
18-35 years old & 295 & 168 & 45 & 508 \\
\hline
36-50 years old & 246 & 123 & 41 & 410 \\
\hline
51-65 years old & 238 & 117 & 48 & 403 \\
\hline
Greater than 65 years old & 137 & 78 & 64 & 279 \\
\hline
Total & 916 & 486 & 198 & 1,600 \\
\hline
\end{tabular}
\end{center}

Which of the following is closest to the difference between the percentage of adults aged 18-50 years who responded "warm" and the percentage of adults aged 51 years or greater who responded "warm"?\\
A. $4 \%$\\
B. $5 \%$\\
C. $10 \%$\\
D. $18 \%$

\section*{ID: 7ed0d098}
Lani spent $15 \%$ of her 8 -hour workday in meetings. How many minutes of her workday did she spend in meetings?\\
A. 1.2\\
B. 15\\
C. 48\\
D. 72

The number $a$ is $70 \%$ less than the positive number $b$. The number $c$ is $60 \%$ greater than $a$. The number $c$ is how many times $b$ ?

The number $a$ is $110 \%$ greater than the number $b$. The number $b$ is $90 \%$ less than 47 . What is the value of $a$ ?

There are 170 blocks in a container. Of these blocks, $10 \%$ are green. How many blocks in the container are green?

\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
 & 1 Star & 2 Stars & 3 Stars & 4 Stars & Total \\
\hline
Employee A & 16 & 49 & 72 & 8 & 145 \\
\hline
Employee B & 4 & 10 & 22 & 34 & 70 \\
\hline
Employee C & 8 & 56 & 45 & 16 & 125 \\
\hline
Employee D & 22 & 42 & 84 & 12 & 160 \\
\hline
Total & 50 & 157 & 223 & 70 & 500 \\
\hline
\end{tabular}
\end{center}

A supervisor at a call center reviewed 500 calls taken by four employees and rated the employees' performance on each call on a scale from 1 star to 4 stars. The ratings for each employee are shown in the table above. According to the table, to the nearest whole percent, what percent of Employee A's calls received a rating of 1 star?\\
A. $3 \%$\\
B. $11 \%$\\
C. $16 \%$\\
D. $32 \%$

\section*{ID: 194ae3b1}
There were approximately 113,000 occupational therapy jobs in the United States in 2012. The Bureau of Labor Statistics has projected that this number will increase by $29 \%$ from 2012 to 2022. Of the following, which is closest to the number of occupational therapy jobs the bureau has projected for the United States in 2022?\\
A. 115,900\\
B. 116,300\\
C. 142,000\\
D. 145,800

\section*{ID: a8fabad0}
A waiter receives tips from each customer. On average, the tip is $15 \%$ of the customer's bill. At this rate, which of the following is closest to the tip the waiter can expect when a customer has a bill that is $\$ 78.20$ ?\\
A. $\$ 8.00$\\
B. $\$ 10.00$\\
C. $\$ 12.00$\\
D. $\$ 14.00$

The number $w$ is $110 \%$ greater than the number $z$. The number $z$ is $55 \%$ less than 50 . What is the value of $w$ ?

432 is $96 \%$ of what number?

\section*{ID: 7b731fc3}
What number is $40 \%$ greater than 115 ?

13 is $p \%$ of 25 . What is the value of $p$ ?

During a sale, the original prices of all the items in a clothing store have been reduced by $20 \%$. What is the sale price of a jacket with an original price of $\$ 50$ ?\\
A. $\$ 12$\\
B. $\$ 30$\\
C. $\$ 36$\\
D. $\$ 40$

\section*{ID: 3d73a58b}
A gift shop buys souvenirs at a wholesale price of 7.00 dollars each and resells them each at a retail price that is $290 \%$ of the wholesale price. At the end of the season, any remaining souvenirs are marked at a discounted price that is $80 \%$ off the retail price. What is the discounted price of each remaining souvenir, in dollars?

What is $10 \%$ of 370 ?\\
A. 27\\
B. 37\\
C. 333\\
D. 360

Thomas installed a new stove in his restaurant. At the time of installation, the stove had a value of $\$ 800$. Thomas estimates that each year the value of the stove will depreciate by $20 \%$ of the previous year's estimated value. What is the estimated value of the stove exactly 2 years after Thomas installed it?\\
A. $\$ 480$\\
B. $\$ 512$\\
C. $\$ 556$\\
D. $\$ 640$

\section*{ID: 6e4a60dd}
Rita's total bill at a restaurant was \$25.00, including tax. If she left a tip of 20\% of the total bill, what was the amount of the tip?\\
A. $\$ 3.50$\\
B. $\$ 4.00$\\
C. $\$ 4.50$\\
D. $\$ 5.00$

\section*{ID: 040f2a84}
The regular price of a shirt at a store is $\$ 11.70$. The sale price of the shirt is $80 \%$ less than the regular price, and the sale price is $30 \%$ greater than the store's cost for the shirt. What was the store's cost, in dollars, for the shirt? (Disregard the \$ sign when entering your answer. For example, if your answer is $\$ 4.97$, enter 4.97)

What number is 20\%\\
greater than 60 ?\\
A. 50\\
B. 72\\
C. 75\\
D. 132

Out of 300 seeds that were planted, $80 \%$ sprouted. How many of these seeds sprouted?

\section*{ID: 8213b1b3}
According to a set of standards, a certain type of substance can contain a maximum of $0.001 \%$ phosphorus by mass. If a sample of this substance has a mass of 140 grams, what is the maximum mass, in grams, of phosphorus the sample can contain to meet these standards?

\section*{ID: 34f8cd89}
$37 \%$ of the items in a box are green. Of those, $37 \%$ are also rectangular. Of the green rectangular items, $42 \%$ are also metal. Which of the following is closest to the percentage of the items in the box that are not rectangular green metal items?\\
A. $1.16 \%$\\
B. $57.50 \%$\\
C. $94.25 \%$\\
D. $98.84 \%$

The number $a$ is $60 \%$ greater than the positive number $b$. The number $c$ is $45 \%$ less than $a$. The number $c$ is how many times $b$ ?

\section*{ID: ad911622}
The value of a collectible comic book increased by $167 \%$ from the end of 2011 to the end of 2012 and then decreased by $16 \%$ from the end of 2012 to the end of 2013 . What was the net percentage increase in the value of the collectible comic book from the end of 2011 to the end of 2013?\\
A. $124.28 \%$\\
B. $140.28 \%$\\
C. $151.00 \%$\\
D. $209.72 \%$


