\section*{ID: 0301c5dc}
The table below shows the number of state parks in a certain state that contain camping facilities and bicycle paths.

\begin{center}
\begin{tabular}{|c|c|c|}
\hline
 & Has bicycle paths & Does not have bicycle paths \\
\hline
Has camping facilities & 20 & 5 \\
\hline
Does not have camping facilities & 8 & 4 \\
\hline
\end{tabular}
\end{center}

If one of these state parks is selected at random, what is the probability that it has camping facilities but does not have bicycle paths?\\
A. $\frac{5}{37}$\\
B. $\frac{5}{25}$\\
C. $\frac{8}{28}$\\
D. $\frac{5}{9}$

\section*{ID: 0ae37ff3}
In a bag, there are 7 red, 4 white, 33 blue, and 33 yellow cubes. If one of these cubes is selected at random, what is the probability of selecting a cube that is neither blue nor yellow?\\
A. $\frac{6}{7}$\\
B. $\frac{7}{11}$\\
C. $\frac{1}{3}$\\
D. $\frac{1}{7}$

The table gives the distribution of votes for a new school mascot and grade level for 80 students.

\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
\multirow[b]{2}{*}{Mascot} & \multicolumn{4}{|c|}{Grade level} \\
\hline
 & Sixth & Seventh & Eighth & Total \\
\hline
Badger & 4 & 9 & 9 & 22 \\
\hline
Lion & 9 & 2 & 9 & 20 \\
\hline
Longhorn & 4 & 6 & 4 & 14 \\
\hline
Tiger & 6 & 9 & 9 & 24 \\
\hline
Total & 23 & 26 & 31 & 80 \\
\hline
\end{tabular}
\end{center}

If one of these students is selected at random, what is the probability of selecting a student whose vote for new mascot was for a lion?\\
A. $\frac{1}{9}$\\
B. $\frac{1}{5}$\\
C. $\frac{1}{4}$\\
D. $\frac{2}{3}$

\section*{ID: 60caadfd}
Each rock in a collection of 70 rocks was classified as either igneous, metamorphic, or sedimentary, as shown in the frequency table.

\begin{center}
\begin{tabular}{|l|c|}
\hline
Classification & Frequency \\
\hline
igneous & 10 \\
\hline
metamorphic & 33 \\
\hline
sedimentary & 27 \\
\hline
\end{tabular}
\end{center}

If one of these rocks is selected at random, what is the probability of selecting a rock that is igneous?\\
A. $\frac{10}{27}$\\
B. $\frac{10}{33}$\\
C. $\frac{10}{60}$\\
D. $\frac{10}{70}$

\section*{ID: e5b5flbdd}
Of the 8 planets in our solar system, 4 are considered rocky. If a student randomly selects 1 of those 8 planets as a topic for a report, what is the probability that the selected planet will be rocky?\\
A. $\frac{1}{8}$\\
B. $\frac{1}{4}$\\
C. $\frac{1}{2}$\\
D. 2

Each vertex of a 14 -sided polygon is labeled with one of the 14 letters $A$ through $N$, with a different letter at each vertex. If one vertex is selected at random, what is the probability that the letter $D$ will be at the selected vertex? (Express your answer as a decimal or fraction, not as a percent.)






















\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Texting behavior & Talks on cell phone daily & Does not talk on cell phone daily & Total \\
\hline
Light & 110 & 146 & 256 \\
\hline
Medium & 139 & 164 & 303 \\
\hline
Heavy & 166 & 74 & 240 \\
\hline
Total & 415 & 384 & 799 \\
\hline
\end{tabular}
\end{center}

In a study of cell phone use, 799 randomly selected US teens were asked how often they talked on a cell phone and about their texting behavior. The data are summarized in the table above. If one of the 799 teens surveyed is selected at random, what is the probability that the teen talks on a cell phone daily?\\
A. $\frac{1}{799}$\\
B. $\frac{415}{799}$\\
C. $\frac{384}{415}$\\
D. $\frac{384}{799}$


A band with 45 members has 11 members who play saxophone. If one band member is selected at random, what is the probability of selecting a band member who plays saxophone?\\
A. $\frac{1}{45}$\\
B. $\frac{11}{45}$\\
C. $\frac{34}{45}$\\
D. $\frac{45}{45}$

\begin{center}
\begin{tabular}{|c|c|c|}
\hline
 & Phone & Email \\
\hline
\begin{tabular}{c}
Dinner \\
dance \\
\end{tabular} & $55 \%$ & $80 \%$ \\
\hline
\begin{tabular}{c}
Football \\
game \\
\end{tabular} & $20 \%$ & $10 \%$ \\
\hline
Picnic & $20 \%$ & $5 \%$ \\
\hline
\begin{tabular}{c}
Pool \\
party \\
\end{tabular} & $5 \%$ & $5 \%$ \\
\hline
Total & $100 \%$ & $100 \%$ \\
\hline
\end{tabular}
\end{center}

An alumni association survey asked each high school graduate to select the one activity he or she preferred for the association's next event. Some of the people responded by phone, and the others responded by email. The table above shows the distribution of preferred activity, in percent, for each response type used. For the survey, the number of email responses was twice the number of phone responses. If a person who preferred a picnic is selected at random, what is the probability that the person responded by email?

\section*{ID: 585de39a}
On May 10, 2015, there were 83 million Internet subscribers in Nigeria. The major Internet providers were MTN, Globacom, Airtel, Etisalat, and Visafone. By September 30, 2015, the number of Internet subscribers in Nigeria had increased to 97 million. If an Internet subscriber in Nigeria on September 30, 2015, is selected at random, the probability that the person selected was an MTN subscriber is 0.43. There were $p$ million MTN subscribers in Nigeria on September 30, 2015. To the nearest integer, what is the value of $p$ ?

\section*{ID: 12dbe3de}
A store received a shipment of $1,000 \mathrm{MP} 3$ players, 4 of which were defective. If an MP3 player is randomly selected from this shipment, what is the probability that it is defective?\\
A. 0.004\\
B. 0.04\\
C. 0.4\\
D. 4

\section*{ID: 912cd125}
For a science project, Anka recorded whether it rained each weekday and weekend day for 12 weeks. Her results are summarized in the table below.\\
Weekday and Weekend Day Rain for 12 Weeks

\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
 & Rain & No rain & Total \\
\hline
Number of weekdays & 12 & 48 & 60 \\
\hline
Number of weekend days & 8 & 16 & 24 \\
\hline
Total & 20 & 64 & 84 \\
\hline
\end{tabular}
\end{center}

If one of the days on which there was no rain is selected at random, what is the probability the day was a weekend day?\\
A. $\frac{4}{21}$\\
B. $\frac{1}{4}$\\
c. $\frac{2}{3}$\\
D. $\frac{3}{4}$

The table summarizes the distribution of age and assigned group for 90 participants in a study.

\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
 & 0-9 years & 10-19 years & 20+ years & Total \\
\hline
Group A & 7 & 14 & 9 & 30 \\
\hline
Group B & 6 & 4 & 20 & 30 \\
\hline
Group C & 17 & 12 & 1 & 30 \\
\hline
Total & 30 & 30 & 30 & 90 \\
\hline
\end{tabular}
\end{center}

One of these participants will be selected at random. What is the probability of selecting a participant from group A, given that the participant is at least 10 years of age? (Express your answer as a decimal or fraction, not as a percent.)

\section*{ID: 30db8f77}
At a conference, there are a total of 275 attendees. Each attendee is assigned to either group $A$, group $B$, or group $C$. If one of these attendees is selected at random, the probability of selecting an attendee who is assigned to group $A$ is 0.44 and the probability of selecting an attendee who is assigned to group $B$ is 0.24 . How many attendees are assigned to group $C$ ?

There are $n$ nonfiction books and 12 fiction books on a bookshelf. If one of these books is selected at random, what is the probability of selecting a nonfiction book, in terms of $n$ ?\\
A. $\frac{n}{12}$\\
B. $\frac{n}{n+12}$\\
C. $\frac{12}{n}$\\
D. $\frac{12}{n+12}$

\section*{ID: 38a9ac45}
If 1,200 customers register for new accounts at a social media website every day, what fraction of the first 60,000 new accounts are registered in the first 5 days?\\
A. $\frac{1}{5}$\\
B. $\frac{1}{10}$\\
C. $\frac{1}{12}$\\
D. $\frac{1}{50}$

\section*{ID: b6569d0e}
United States\\
Presidents\\
from 1789 to\\
2015

\begin{center}
\begin{tabular}{|c|c|}
\hline
Ages & Number \\
\hline
$40-44$ & 2 \\
\hline
$45-49$ & 7 \\
\hline
$50-54$ & 13 \\
\hline
$55-59$ & 11 \\
\hline
$60-64$ & 7 \\
\hline
$65-69$ & 3 \\
\hline
\end{tabular}
\end{center}

The table above gives the number of United States presidents from 1789 to 2015 whose age at the time they first took office is within the interval listed. Of those presidents who were at least 50 years old when they first took office, what fraction were at least 60 years old?\\
A. $\frac{10}{43}$\\
B. $\frac{10}{34}$\\
C. $\frac{10}{24}$\\
D. $\frac{25}{34}$

\section*{ID: 5dc386fb}
The table below shows the distribution of US states according to whether they have a state-level sales tax and a state-level income tax.

2013 State-Level Taxes

\begin{center}
\begin{tabular}{|c|c|c|}
\hline
 & State sales tax & No state sales tax \\
\hline
State income tax & 39 & 4 \\
\hline
No state income tax & 6 & 1 \\
\hline
\end{tabular}
\end{center}

To the nearest tenth of a percent, what percent of states with a state-level sales tax do not have a state-level income tax?\\
A. $6.0 \%$\\
B. $12.0 \%$\\
C. $13.3 \%$\\
D. $14.0 \%$

\section*{ID: b8150b17}
For a particular machine that produces beads, 29 out of every 100 beads it produces have a defect. A bead produced by the machine will be selected at random. What is the probability of selecting a bead that has a defect?\\
A. $\frac{1}{2,900}$\\
B. $\frac{1}{29}$\\
C. $\frac{29}{100}$\\
D. $\frac{29}{10}$

\section*{ID: 1dcea480}
A bag contains a total of 60 marbles. A marble is to be chosen at random from the bag. If the probability that a blue marble will be chosen is 0.35 , how many marbles in the bag are blue?\\
A. 21\\
B. 25\\
C. 35\\
D. 39

\section*{ID: a3384df0}
Penguin Exhibit

\begin{center}
\begin{tabular}{|c|r|r|r|}
\hline\hline
Type of penguin & Male & Female & Total \\
\hline
Chinstrap & 41 & 59 & 100 \\
\hline
Emperor & 8 & 27 & 35 \\
\hline
Gentoo & 49 & 54 & 103 \\
\hline
Macaroni & 42 & 40 & 82 \\
\hline
Total & 140 & 180 & 320 \\
\hline
\end{tabular}
\end{center}

The number of penguins in a zoo exhibit, sorted by gender and type of penguin, is shown in the table above. Which type of penguin has a female population that is the closest to being $\frac{1}{3}$ of the total female penguin population in the exhibit?\\
A. Chinstrap\\
B. Emperor\\
C. Gentoo\\
D. Macaroni

There are 20 buttons in a bag: 8 white buttons, 2 orange buttons, and 10 brown buttons. If one of these buttons is selected at random, what is the probability of selecting a white button?\\
A. $\frac{2}{20}$\\
B. $\frac{8}{20}$\\
C. $\frac{10}{20}$\\
D. $\frac{12}{20}$

A box contains 13 red pens and 37 blue pens. If one of these pens is selected at random, what is the probability of selecting a red pen? (Express your answer as a decimal or fraction, not as a percent.)

\section*{ID: f8696cd8}
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
 & Human Resources & Accounting \\
\hline
Bachelor's degree & 4 & 3 \\
\hline
Master's degree & 2 & 6 \\
\hline
\end{tabular}
\end{center}

The table above shows the number of people who work in the Human Resources and Accounting departments of a company and the highest level of education they have completed. A person from one of these departments is to be chosen at random. If the person chosen works in the Human Resources department, what is the probability that the highest level of education the person completed is a master's degree?\\
A. $\frac{2}{15}$\\
B. $\frac{1}{3}$\\
C. $\frac{1}{4}$\\
D. $\frac{8}{15}$

\section*{ID: ecd09c38}
Employees working for a customer service line at an electric company recorded all the calls last Monday and noted whether the caller asked for repairs and whether the caller asked about a bill. The results are summarized in the table below.

\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
 & \begin{tabular}{c}
Asked for \\
repairs \\
\end{tabular} & \begin{tabular}{c}
Did not ask \\
for repairs \\
\end{tabular} & Total \\
\hline
\begin{tabular}{c}
Asked \\
about a bill \\
\end{tabular} & 48 & 623 & 671 \\
\hline
\begin{tabular}{c}
Did not ask \\
about a bill \\
\end{tabular} & 130 & 90 & 220 \\
\hline
Total & 178 & 713 & 891 \\
\hline
\end{tabular}
\end{center}

If a caller last Monday who asked about his or her bill is selected at random, which of the following is closest to the probability that the customer also asked for repairs?\\
A. 0.05\\
B. 0.07\\
C. 0.20\\
D. 0.27

The table summarizes the distribution of color and shape for 100 tiles of equal area.

\begin{center}
\begin{tabular}{|l|c|c|c|c|}
\hline
 & Red & Blue & Yellow & Total \\
\hline
Square & 10 & 20 & 25 & 55 \\
\hline
Pentagon & 20 & 10 & 15 & 45 \\
\hline
Total & 30 & 30 & 40 & 100 \\
\hline
\end{tabular}
\end{center}

If one of these tiles is selected at random, what is the probability of selecting a red tile? (Express your answer as a decimal or fraction, not as a percent.)


